\titledquestion{Choose an Algorithm}

You are given a list of questions where you need to find an algorithm to solve each of them. If multiple algorithms apply, choose the most efficient one.  

The algorithms that you can choose from are:\\ 
A. BFS ~ B. Topological Sort ~ C. Dijkstra's Algorithm \\ D. Bellman-Ford Algorithm ~ E. A* Search Algorithm

Write the index (A,B,C,...) in the blank.
% For LaTeX user, just write A,B,C,... in the "[]" of "\fillin[]".

\begin{parts}

\part[1] Given a graph with probably negative edge weights, we want to know whether there is a negative cycle, i.e. a cycle such that its edge weights sum up to negative. 
\fillin[\hspace{1cm}]

\part[1] This is a modified version of the Travelling salesman problem. There are $n$ points on 2D a plane. The trajectory of length $k$ is an ordered sequence $(a_1,a_2,\ldots, a_k)$ where $a_i$ refers to a point. The length of a trajectory is $\sum_{i=1}^{k-1} dis(a_i,a_{i+1})$. We want to find the shortest trajectory of length $k$. 
\fillin[\hspace{1cm}]

\part[1] Given a graph and a source vertex $s$, we want to find the vertices that can be reached from $s$ through no more than $k$ edges. 
\fillin[\hspace{1cm}]

\part[1] Given a DAG with probably negative edge weight and a source vertex $s$, we want to find the shortest path from $s$ to every vertex. 
\fillin[\hspace{1cm}]

\part[1] Given a directed graph with non-negative edge weights and a source vertex $s$, we want to find the shortest path from $s$ to every vertex. 
\fillin[\hspace{1cm}]

\part[1] There is a signal source in a 2D grid. You have a sensor that tells the distance between you and the signal source but the number is noisy, i.e. it may not be exactly correct but is close to the real distance. You start from a grid and can go to an adjacent grid each time. We want to find the signal source in shortest time.
\fillin[\hspace{1cm}]

\part[1] Given a undirected graph, we want to check whether it is a bipartite graph.
\fillin[\hspace{1cm}]




\end{parts}

