\titledquestion{Multiple Choices}

Each question has \textbf{one or more} correct answer(s). Select all the correct answer(s). For each question, you will get 0 points if you select one or more wrong answers, but you will get 1 point if you select a non-empty subset of the correct answers.

Write your answers in the following table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Note: The `LaTeX' way to answer a multiple-choices question is to replace `\choice'
% with `\CorrectChoice', as what you did in the previous questions. However, there are 
% still many students who would like to handwrite their homework. To make TA's work 
% easier, you have to fill your selected choices in the table below, no matter whether 
% you use LaTeX or not.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[htbp]
    \centering
    \begin{tabular}{|p{2cm}|p{2cm}|p{2cm}|}
        \hline
        (a) & (b) \\
        \hline
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        % YOUR ANSWER HERE.
          &     \\
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \hline
    \end{tabular}
\end{table}

\begin{parts}
\part[2] Consider an AVL tree whose number of nodes is $n$ and height is $h$, which of the following are true?

    \begin{choices}
        \choice $n=O(2^h)$.
        \choice $n=O(\alpha^h)$, where $\alpha = \dfrac{1+\sqrt{5}}{2}$.
        \choice $h$ is always not greater than the height of a BST with $n$ nodes.
        \choice $h=\Theta(\log n)$ in all cases.
    \end{choices}
    
    \part[2] Which of the following statements are true for an AVL tree? Here one balance correction means a single rotation (in left-left or right-right cases) or a double rotation (in left-right or right-left cases).
    
    \begin{choices}
        \choice Inserting an item causes at most one node imbalanced before checking if any balance correction is needed.
        \choice At most one balance correction has to be performed after inserting an item.
        \choice Removing an item in leaf nodes causes at most one node imbalanced before checking if any balance correction is needed.
        \choice At most one balance correction has to be performed after removing an item.
    \end{choices}
    
\end{parts}