\titledquestion{Multiple Choices}

Each question has \textbf{one or more} correct answer(s). Select all the correct answer(s). For each question, you will get 0 points if you select one or more wrong answers, but you will get 1 point if you select a non-empty subset of the correct answers.

Write your answers in the following table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Note: The `LaTeX' way to answer a multiple-choices question is to replace `\choice'
% with `\CorrectChoice', as what you did in the first question. However, there are still
% many students who would like to handwrite their homework. To make TA's work easier,
% you have to fill your selected choices in the table below, no matter whether you use 
% LaTeX or not.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[htbp]
    \centering
    \begin{tabular}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
        \hline
        (a) & (b) & (c) & (d) & (e) & (f) \\
        \hline
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        % YOUR ANSWER HERE.
        &     &     &     &     &     \\
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \hline
    \end{tabular}\label{tab:multiple}
\end{table}

\begin{parts}
    \part[2] Which of the following statements is/are true about \textbf{tree}?

    \begin{choices}
        \choice A tree with $N$ nodes has $N-1$ edges.
        \choice The height of a tree is always positive.
        \choice Every node of a tree is either a leaf node or an internal node.
        \choice The degree and the depth of the root node should be $0$.
    \end{choices}

    \part[2] Which of the following statements is/are true about \textbf{binary tree}?

    \begin{choices}
        \choice In a binary tree, every non-root node has exactly one parent.
        \choice Every full binary tree is also a complete binary tree.
        \choice A full binary tree with $n$ non-leaf nodes contains $2n - 1$ total nodes.
        \choice A binary tree of height $0$ is also perfect.
    \end{choices}

    \part[2] Which of the following choices is/are $\Theta(m)$ where $m$ is the maximum length of the queue when traversing a tree with BFS?

    \begin{choices}
        \choice The total number of nodes in the tree.
        \choice The length of the deepest path from a leaf node to the root node.
        \choice The maximum degree of nodes in the tree.
        \choice The maximum number of nodes at a given depth of the tree.
    \end{choices}

    \part[2] There exists two paths between any two different nodes in a tree with height more than 3.

    \begin{choices}
        \choice True.
        \choice False.
    \end{choices}

    \part[2] The height of a tree is always equal to the maximum depth of nodes in the tree.

    \begin{choices}
        \choice True.
        \choice False.
    \end{choices}

    \part[2] Which of the following statements is/are false?

    \begin{choices}
        \choice Nodes with the same depth are siblings.
        \choice Each node in the tree has exactly one parent pointing to it.
        \choice Given any node $\alpha$ within a tree, the collection of $\alpha$ and all of its descendants is a subtree of the tree with root $\alpha$.
        \choice The root node cannot be the descendent of any nodes.
    \end{choices}

\end{parts}