\titledquestion{Multiple Choices}

Each question has \textbf{one or more} correct answer(s). Select all the correct answer(s). For each question, you will get 0 points if you select one or more wrong answers, but you will get 1 point if you select a non-empty subset of the correct answers.

Write your answers in the following table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Note: The `LaTeX' way to answer a multiple-choices question is to replace `\choice'
% with `\CorrectChoice', as what you did in the first question. However, there are still
% many students who would like to handwrite their homework. To make TA's work easier,
% you have to fill your selected choices in the table below, no matter whether you use 
% LaTeX or not.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[htbp]
	\centering
	\begin{tabular}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
		\hline 
		(a) & (b) & (c) & (d) \\
		\hline
  		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		% YOUR ANSWER HERE.
		&  &  &  \\
            %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\hline
	\end{tabular} 
\end{table}

\begin{parts}
	\part[2] Which of the following operations on a \textbf{Linked List} take constant time?

	\begin{choices}
		\choice Given a pointer $h$ which points  to the head node of a linked list, we want to erase the head node.
		\choice Given a pointer $h$ which points to the head node of a linked list, we want to gain access to the last element of the linked list.
		\choice Given a pointer $p$ which points to a node in a linked list, we want to gain access the previous node of $p$.
		\choice Given a pointer $p$ which points to a node in a linked list, we want to insert an element after $p$.
	\end{choices}

        \part[2] Which of the following statements about arrays and linked-lists are true?

        \begin{choices}
            \choice Inserting an element into the middle of an array takes constant time.
            \choice A doubly linked list consumes more memory than a (singly) linked list of the same length.
            \choice Given a pointer to some node in a doubly linked list, we are able to gain access to every node of it.
            \choice Given a pointer to any node in a linked list, we are able to gain access to the last node. 
        \end{choices}

        \part[2] Please evaluate the following reverse-Polish expressions. Which of them are legal reverse-Polish expressions and gives a result greater than 0?

        \begin{choices}
            \choice \ttt{2 3 2 * + 1 /}
            \choice \ttt{1 2 4 - - 3 *}
            \choice \ttt{1 * 2 - 1 + 5}
            \choice \ttt{2 4 3 1 + * -}
        \end{choices}

        \part[2] Assume we implement a queue with a circular array indexed from $0$ to $n-1$. Now the \ttt{front} pointer is at index $a$, and the \ttt{back} pointer is at index $b$. Which of the following best describes the number of the elements in the queue?

        \begin{choices}
            \choice $b-a+1$
            \choice $|b-a+1|$
            \choice $b-a+1+n$
            \choice $(b-a+1+n) \mod n$
        \end{choices}


\end{parts}